Supplementary Information: Joint effects of climate, tree size, and year on annual tree growth derived from tree-ring records of ten globally distributed forests (Anderson-Teixeira et al., *GCB*)

### 2021-10-25 doc/manuscript/ForestGEO_treerings_SI.Rmd
better title for SI

---
title: "Supplementary Information"
author:
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: references.bib
csl: global-change-biology.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---

>>>>

---
title: "Supplementary Information: Joint effects of climate, tree size, and year on annual tree growth derived from tree-ring records of ten globally distributed forests (Anderson-Teixeira et al., *GCB*)"
author:
output: 
  pdf_document:
    fig_caption: yes
    toc: true # table of content true
    toc_depth: 2  
bibliography: references.bib
csl: global-change-biology.csl
header-includes:  \usepackage{float}
                  \usepackage{caption}
                  \captionsetup[table]{font=footnotesize}
                  \captionsetup[figure]{font=footnotesize}
                  \captionsetup[figure]{labelformat=empty}
                  \captionsetup[table]{labelformat=empty}
                  \usepackage{pdflscape}
                  \newcommand{\blandscape}{\begin{landscape}}
                  \newcommand{\elandscape}{\end{landscape}}
---
